Interpolate the weight at agecl output to annual age

### 2020-06-02 InterpolateWeightAtAge.Rmd
computes avg age of agecl, agecl and time-specific avg wt increment

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(tidyverse)
library(atlantisom)

@@

wtagecl <- wtage

calc_wtTrueage <- function(wtagecl, fgs) {
  # get number of ages per agecl from fgs.file
  #fgs <- atlantisom::load_fgs(dir=d.name, file_fgs = functional.groups.file)
  species.code <- fgs$Code
  #turnedon <- fgs[fgs$IsTurnedOn > 0, ]

@@

  # make a dataframe the right dimensions for all age classes
  wtage_out <- data.frame()

  # find weight increment for a timestep
  # muweight for agecl+1 - muweight for agecl

  # divide weight increment by number of ages per agecl (could decay with increasing age, but how different from equal increment?)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(tidyverse)
library(atlantisom)
library(ggthemes)

@@

wtagecl <- wtage
annages <- NOBAom_cod$truenumsage_ss %>%
  group_by(species, time, agecl) %>%
  rename(trueage = agecl) %>%
  summarise(truenatage = sum(atoutput))

calc_wtTrueage <- function(wtagecl, annages, fgs) {
  # get number of ages per agecl from fgs.file
  #fgs <- atlantisom::load_fgs(dir=d.name, file_fgs = functional.groups.file)
  species.code <- fgs$Code
  #turnedon <- fgs[fgs$IsTurnedOn > 0, ]

@@

  # make a dataframe the right dimensions for all age classes
  # has species, time from wtage and trueage, truenatage from annages
  # add agecl column
  # finds the average age of each agecl each timestep based on truenatage
  wtage_out <- annages %>%
    dplyr::semi_join(wtagecl, by = c("species", "time")) %>%
    dplyr::left_join(multiple_ages, by = c("species" = "Name")) %>%
    dplyr::mutate(agecl = as.integer(ceiling(trueage/NumAgeClassSize))) %>%
    dplyr::group_by(species, time, agecl) %>%
    dplyr::mutate(avgage = weighted.mean(trueage, truenatage))

  # find weight increment for a timestep
  # muweight for agecl+1 - muweight for agecl
  wtagecl_inc <- wtagecl %>%
    dplyr::arrange(species, time, agecl) %>%
    dplyr::left_join(multiple_ages, by = c("species" = "Name")) %>%
    dplyr::group_by(species, time) %>%
    dplyr::mutate(increment = case_when(
      agecl==1 ~ atoutput,
      agecl>1 ~ atoutput - dplyr::lag(atoutput)
      )) %>%
    dplyr::mutate(agewtinc = increment/NumAgeClassSize)

  # last line above does this: divide weight increment by number of ages per agecl 
  # definitely wrong, especially at younger ages, for two reasons:
  #  - assumes each agecl has equal numbers of its constituent ages
  #  - assumes linear growth between age classes
  # (could decay with increasing age, but how different from equal increment?)
  # avgWtAge for agecl 1 = (n age1 * avgwt age1) + (n age2 * avgwt age2)
